Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
figures moved around

% added by tbm
\usepackage{subfloat,subfig}
\setlength{\abovecaptionskip}{-3pt}
\setlength{\belowcaptionskip}{10pt}

@@

One major issue in working with small patches concerns temporal
alignment. Learning the same motifs with different offset
(of a few seconds, or audio frames) is redundant. We take advantage
of rhythmic knowledge about the song to align patches with beats.
We can further group beats into bars, meaningful music segments.
The use of the Echo Nest API \cite{EchoNest} for that purpose is 
explained in Subsection \ref{ssec:beatpatch}. Patches built around
those temporal landmarks should capture music motifs more easily.

@@

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.99\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a codeword or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $0$ (just initialization) to $500$ thousand. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.
}}
\label{fig:data_sizes}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{encoding_per_beat}
\end{center}
\caption{\small{Encoding larger and larger patterns with a fixed size
codebook. The size of the pattern is defined by the number of beats,
the bar information was not taken into account for this experiment.
}}
\label{fig:perbeat}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.7\columnwidth]{freqs}
\end{center}
\caption{\small{ Usage frequency of the patterns in the codebook from
    Figure \ref{fig:codes1} on the artist20 dataset.  There are $71,832$
    patterns in total in the dataset.  Note that all codes were
    initialized with a random sample from the training set and might
    not be used in this test set.
    FIXME: so why not show usage in training data?  I think test.mat
    should contain this information.
  }}
\label{fig:freqs}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfloat[][\small{Metallica}]{\label{fig:metallica2}\includegraphics[width=0.35\columnwidth]{metallica_pattern}}
  \hspace{5mm}                
  \subfloat[][\small{Tori Amos / Suzanne Vega}]{\label{fig:amosvega2}\includegraphics[width=0.35\columnwidth]{toriamos_suzannevega_pattern}}
  \caption{\small{Typical patterns for different artists.}}
  \label{fig:typicalpat}
\end{figure}

>>>>

% added by tbm
\usepackage{subfloat,subfig}
\setlength{\abovecaptionskip}{-3pt}
\setlength{\belowcaptionskip}{6pt}

@@

One major issue in working with small patches concerns temporal
alignment. Learning the same motifs with different offset
(of a few seconds, or audio frames) is redundant. We take advantage
of rhythmic knowledge about the song to align patches with beats.
We can further group beats into bars to produces patches
for meaningful music segments.
The use of the Echo Nest API \cite{EchoNest} for that purpose is 
explained in Subsection \ref{ssec:beatpatch}. Patches built around
those temporal landmarks should capture music motifs more easily.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{data_sizes}
\end{center}
\caption{\small{Distortion for a codebook of size $100$ encoding one bar
at a time, a bar being represented by $4$ chroma feature vector.
Therefore, a codeword or a pattern is of size $12$ x $4$ = $48$.
Distortion measure on the test data set. Data size tested range
from $0$ (just initialization) to $500$ thousand. Patterns were selected at
random from the dataset of approximately $3,7$ million patterns.
}}
\label{fig:data_sizes}
\end{figure}

@@

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{encoding_per_beat}
\end{center}
\caption{\small{Encoding larger and larger patterns with a fixed size
codebook. The size of the pattern is defined by the number of beats,
the bar information was not taken into account for this experiment.
}}
\label{fig:perbeat}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.6\columnwidth]{freqs}
\end{center}
\caption{\small{ Usage frequency of the patterns in the codebook from
    Figure \ref{fig:codes1} on the artist20 dataset.  There are $71,832$
    patterns in total in the dataset.  Note that all codes were
    initialized with a random sample from the training set and might
    not be used in this test set.
    FIXME: so why not show usage in training data?  I think test.mat
    should contain this information.
  }}
\label{fig:freqs}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfloat[][\small{Metallica}]{\label{fig:metallica2}\includegraphics[width=0.32\columnwidth]{metallica_pattern}}
  \hspace{5mm}                
  \subfloat[][\small{Tori Amos / Suzanne Vega}]{\label{fig:amosvega2}\includegraphics[width=0.32\columnwidth]{toriamos_suzannevega_pattern}}
  \caption{\small{Typical patterns for different artists.}}
  \label{fig:typicalpat}
\end{figure}
